Wigglyhedra

### 2025-02-14 wigglyAligned/wigglyhedra.tex
minor correction acknowledgments

\thanks{AB was partially supported by the Australian Research Council DECRA grant DE240100447. 
  VP was partially supported by the Spanish grant PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), by the French grant CHARMS (ANR-19-CE40-0017), and by the French--Austrian projects PAGCAP (ANR-21-CE48-0020 \& FWF~I~5788).}

@@

\centerline{\includegraphics[scale=1.75]{wigglyFlipGraph}}

@@

Also record the following statements for future use; the first may be found in~\cite[Sect.~1.3]{bel.ber.del:82}

>>>>

\thanks{AB was partially supported by the Australian Research Council DECRA grant DE240100447. 
VP was partially supported by the Spanish project PID2022-137283NB-C21 of MCIN/AEI/10.13039/501100011033 / FEDER, UE, by the Spanish--German project COMPOTE (AEI PCI2024-155081-2 \& DFG 541393733), by the Severo Ochoa and María de Maeztu Program for Centers and Units of Excellence in R\&D (CEX2020-001084-M), by the Departament de Recerca i Universitats de la Generalitat de Catalunya (2021 SGR 00697), and by the French--Austrian project PAGCAP (ANR-21-CE48-0020 \& FWF I 5788).}

@@

\centerline{\includegraphics[scale=1.7]{wigglyFlipGraph}}

@@

Also record the following statements for future use; the first may be found in~\cite[Sect.~1.3]{bel.ber.del:82}.
